---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
totalSteps = aggregate(steps ~ date, data = data, sum, na.rm = TRUE)
hist(totalSteps$steps, breaks = 20, main="Total number of steps take per day")
meanSteps <- mean(totalSteps$steps)
medianSteps <- median(totalSteps$steps)
```

Mean number of steps takne per day: `round(meanSteps)`

Mean number of steps takne per day: `medianSteps`


## What is the average daily activity pattern?

Average steps by time interval across all days

```{r}
stepsByInterval <- aggregate(steps ~ interval, data=data, mean, na.rm = TRUE)
plot(steps ~ interval, data=stepsByInterval, type="l", main="Average steps taken per Interval")
```


```{r}
maxInterval <- stepsByInterval[which.max(stepsByInterval$steps),1]
```

The 5-minute interval that, on average, contains the maximum number of steps: `maxInterval`


## Imputing missing values

Create additional column to set mean steps per interval

```{r}
dataWithMean <- cbind(data, meanSteps = stepsByInterval$steps)
dataWithNoNA <- data.frame(steps = ifelse(is.na(dataWithMean$steps), dataWithMean$meanSteps, dataWithMean$steps), date = dataWithMean$date, inteval = dataWithMean$interval)
totalStepsWithNoNA = aggregate(steps ~ date, data = dataWithNoNA, sum)
hist(totalStepsWithNoNA$steps, breaks = 20, main="Total number of steps take per day")
meanStepsWithNoNA <- mean(totalStepsWithNoNA$steps)
medianStepsWithNoNA <- median(totalStepsWithNoNA$steps)
```

Mean number of steps taken per day with no NA: `round(meanStepsWithNoNA)`

Mean number of steps taken per day with no NA: `medianStepsWithNoNA`



## Are there differences in activity patterns between weekdays and weekends?

```{r}
dataWithNoNA$date <- strptime(dataWithNoNA$date, "%Y-%m-%d")
dataWithNoNA$weekend <- (weekdays(dataWithNoNA$date) %in% c("Sunday", "Saturday"))
weekend <- dataWithNoNA[dataWithNoNA$weekend == TRUE,]
weekday <- dataWithNoNA[dataWithNoNA$weekend == FALSE,]
weekendSteps <- aggregate(steps ~ inteval, weekend, mean)
weekdaySteps <- aggregate(steps ~ inteval, weekday, mean)
par(mfrow=c(1,2))
plot(steps ~ inteval, data=weekendSteps, type="l", main="Average steps taken per Interval in Weekends")
plot(steps ~ inteval, data=weekdaySteps, type="l", main="Average steps taken per Interval in Weekdays")


```
